ANOVA Comparison Simulations: Skewed, Poisson Data

### 2016-12-07 simulations/simulation.Rmd
Create power summary tables

>>>>

```{r power_summary_tab, results = "asis"}
summary05 <- t(sapply(powers, function(x) x[5, c(6, 7, 1:5)]))
summarytab <- xtable(summary05, align = "rp{1.25in}|p{0.7in}|p{0.6in}p{0.8in}p{0.8in}p{0.8in}p{0.75in}",
       caption = "Empirical power at level $0.05$ for Gaussian simulated data")
print(summarytab, type="latex", file="../ms/fig/normal_simulation_power_summary.tex")
summarytab
```

### 2016-12-07 simulations/simulation_skewed.Rmd
Create power summary tables

>>>>

```{r power_summary_tab, results = "asis"}
summary05 <- t(sapply(powers, function(x) x[5, c(6, 7, 1:5)]))
summarytab <- xtable(summary05, align = "rp{1.25in}|p{0.7in}|p{0.6in}p{0.8in}p{0.8in}p{0.8in}p{0.75in}",
       caption = "Empirical power at level $0.05$ for discrete, skewed simulated data")
print(summarytab, type="latex", file="../ms/fig/skewed_simulation_power_summary.tex")
summarytab
```
